### 2023-01-13 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@1fd7f0c201ea0f03820cb55e1349980d2ccbea5b 🚀

\vfill
\textbf{\sffamily Abstract: }Food webs are complex ecological networks
whose structure is both ecologically and statistically constrained, with
many network properties being correlated with each other. Despite the
recognition of these invariable relationships in food webs, the use of
the principle of maximum entropy (MaxEnt) in network ecology is still
rare. This is surprising considering that MaxEnt is a renowned and
rigorous statistical tool precisely designed for understanding and
predicting many different types of constrained systems. Precisely, this
principle asserts that the least-biased probability distribution of a
system's property, constrained by prior knowledge about that system, is
the one with maximum information entropy. MaxEnt has been proven useful
in many ecological modelling problems, but its application in food webs
and other ecological networks is limited. Here we show how MaxEnt can be
used to derive many food-web properties both analytically and
heuristically. First, we show how the joint degree distribution (the
joint probability distribution of the numbers of prey and predators for
each species in the network) can be derived analytically using the
number of species and the number of interactions in food webs. Second,
we present a heuristic and flexible approach of finding a network's
adjacency matrix (the network's representation in matrix format) based
on simulated annealing and SVD entropy. We built two heuristic models
using the connectance and the joint degree sequence as statistical
constraints, respectively. We compared both models' predictions against
corresponding null and neutral models commonly used in network ecology
using open access data of terrestrial and aquatic food webs sampled
globally (N = 257). We found that the heuristic model constrained by the
joint degree sequence was a good predictor of many measures of food-web
structure, especially the nestedness and motifs distribution.
Specifically, our results suggest that the structure of terrestrial and
aquatic food webs is mainly driven by their joint degree distribution.
\vfill

>>>>

\vfill
\textbf{\sffamily Abstract: }Food webs are complex ecological networks
whose structure is both ecologically and statistically constrained, with
many network properties being correlated with each other. Despite the
recognition of these invariable relationships in food webs, the use of
the principle of maximum entropy (MaxEnt) in network ecology is still
rare. This is surprising considering that MaxEnt is a statistical tool
precisely designed for understanding and predicting many different types
of constrained systems. Precisely, this principle asserts that the
least-biased probability distribution of a system's property,
constrained by prior knowledge about that system, is the one with
maximum information entropy. MaxEnt has been proven useful in many
ecological modelling problems, but its application in food webs and
other ecological networks is limited. Here we show how MaxEnt can be
used to derive many food-web properties both analytically and
heuristically. First, we show how the joint degree distribution (the
joint probability distribution of the numbers of prey and predators for
each species in the network) can be derived analytically using the
number of species and the number of interactions in food webs. Second,
we present a heuristic and flexible approach of finding a network's
adjacency matrix (the network's representation in matrix format) based
on simulated annealing and SVD entropy. We built two heuristic models
using the connectance and the joint degree sequence as statistical
constraints, respectively. We compared both models' predictions against
corresponding null and neutral models commonly used in network ecology
using open access data of terrestrial and aquatic food webs sampled
globally (N = 257). We found that the heuristic model constrained by the
joint degree sequence was a good predictor of many measures of food-web
structure, especially the nestedness and motifs distribution.
Specifically, our results suggest that the structure of terrestrial and
aquatic food webs is mainly driven by their joint degree distribution.
\vfill

### 2023-01-13 preprint.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@1fd7f0c201ea0f03820cb55e1349980d2ccbea5b 🚀

\textbf{Abstract}:\,Food webs are complex ecological networks whose
structure is both ecologically and statistically constrained, with many
network properties being correlated with each other. Despite the
recognition of these invariable relationships in food webs, the use of
the principle of maximum entropy (MaxEnt) in network ecology is still
rare. This is surprising considering that MaxEnt is a renowned and
rigorous statistical tool precisely designed for understanding and
predicting many different types of constrained systems. Precisely, this
principle asserts that the least-biased probability distribution of a
system's property, constrained by prior knowledge about that system, is
the one with maximum information entropy. MaxEnt has been proven useful
in many ecological modelling problems, but its application in food webs
and other ecological networks is limited. Here we show how MaxEnt can be
used to derive many food-web properties both analytically and
heuristically. First, we show how the joint degree distribution (the
joint probability distribution of the numbers of prey and predators for
each species in the network) can be derived analytically using the
number of species and the number of interactions in food webs. Second,
we present a heuristic and flexible approach of finding a network's
adjacency matrix (the network's representation in matrix format) based
on simulated annealing and SVD entropy. We built two heuristic models
using the connectance and the joint degree sequence as statistical
constraints, respectively. We compared both models' predictions against
corresponding null and neutral models commonly used in network ecology
using open access data of terrestrial and aquatic food webs sampled
globally (N = 257). We found that the heuristic model constrained by the
joint degree sequence was a good predictor of many measures of food-web
structure, especially the nestedness and motifs distribution.
Specifically, our results suggest that the structure of terrestrial and
aquatic food webs is mainly driven by their joint degree distribution.

>>>>

\textbf{Abstract}:\,Food webs are complex ecological networks whose
structure is both ecologically and statistically constrained, with many
network properties being correlated with each other. Despite the
recognition of these invariable relationships in food webs, the use of
the principle of maximum entropy (MaxEnt) in network ecology is still
rare. This is surprising considering that MaxEnt is a statistical tool
precisely designed for understanding and predicting many different types
of constrained systems. Precisely, this principle asserts that the
least-biased probability distribution of a system's property,
constrained by prior knowledge about that system, is the one with
maximum information entropy. MaxEnt has been proven useful in many
ecological modelling problems, but its application in food webs and
other ecological networks is limited. Here we show how MaxEnt can be
used to derive many food-web properties both analytically and
heuristically. First, we show how the joint degree distribution (the
joint probability distribution of the numbers of prey and predators for
each species in the network) can be derived analytically using the
number of species and the number of interactions in food webs. Second,
we present a heuristic and flexible approach of finding a network's
adjacency matrix (the network's representation in matrix format) based
on simulated annealing and SVD entropy. We built two heuristic models
using the connectance and the joint degree sequence as statistical
constraints, respectively. We compared both models' predictions against
corresponding null and neutral models commonly used in network ecology
using open access data of terrestrial and aquatic food webs sampled
globally (N = 257). We found that the heuristic model constrained by the
joint degree sequence was a good predictor of many measures of food-web
structure, especially the nestedness and motifs distribution.
Specifically, our results suggest that the structure of terrestrial and
aquatic food webs is mainly driven by their joint degree distribution.
